% Academic CV - Mary Ogunmola
\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}
\usepackage{parskip}
\usepackage[hidelinks]{hyperref}
\usepackage{array}
\usepackage{ragged2e}
\usepackage{enumitem}

% Convenience command: left-date column width
\newlength{\DateCol}
\setlength{\DateCol}{1.2in}

% Entry: two-column row with date on left and content on right
\newcommand{\entry}[2]{%
  \noindent\begin{tabular}{@{}p{\DateCol} p{\dimexpr\linewidth-\DateCol\relax}@{}}%
    \raggedright #1 & \raggedright #2
  \end{tabular}\par\vspace{4pt}%
}

\begin{document}

% ================ HEADER ================
\begin{center}
    {\LARGE\bfseries Mary Ogunmola}
\end{center}

\vspace{6pt}

\noindent
\begin{tabular}{@{}p{0.58\linewidth} p{0.48\linewidth}@{}}
MEB Room 3490A & Email: \href{mailto:mary.ogunmola@utah.edu}{mary.ogunmola@utah.edu} \\
50 South Central Campus Drive & Phone: +1 (385) 443-9712 \\
Salt Lake City, UT 84112 & LinkedIn: \href{https://www.linkedin.com/in/mary-ogunmola-8a85141b0/}{linkedin.com/in/mary-ogunmola} \\
& GitHub: \href{https://github.com/maryayobami}{github.com/maryayobami} \\
\end{tabular}

\rule{\linewidth}{0.4pt}

% ================ EDUCATION ================
\section*{EDUCATION}

\entry{\textbf{Ph.D.,}}{%
\textbf{University of Utah} \\
Computer Science (expected 2030) \\
Advisor: Professor Robert Ricci. \\
Research areas: Distributed systems; Confidential computing; Cloud security; 5G networks.
}

\entry{\textbf{B.Sc.,}}{%
\textbf{Joseph Ayo Babalola University} \\
Computer Science (2023) \\
Thesis: \textit{Development of a Mobile-Based Courseware to Improve Accessibility of Academic Resources.}
}

% ================ RESEARCH INTERESTS ================
\section*{RESEARCH INTERESTS}

\entry{}{Distributed systems; Cloud computing; Virtualization; Cloud security; Confidential computing; 5G networks.}

% ================ RESEARCH EXPERIENCE ================
\section*{RESEARCH EXPERIENCE}

\entry{\textbf{2025 -- Present}}{%
\textbf{Graduate Research Assistant}, Flux Research Group, University of Utah. \\
Advisor: Professor Robert Ricci.
\begin{itemize}[leftmargin=*, nosep, itemsep=1pt]
    \item Investigating hardware-assisted security mechanisms for 5G network functions in cloud environments
    \item Designing Kubernetes-based benchmarking framework to evaluate latency and performance overhead
\end{itemize}
}

\entry{\textbf{2023 -- 2024}}{%
\textbf{Undergraduate Research Assistant}, Joseph Ayo Babalola University. \\
Advisor: V. A. Olutayo.
\begin{itemize}[leftmargin=*, nosep, itemsep=1pt]
    \item Developed unified academic resource database and cross-platform app (120\% accessibility improvement)
    \item Conducted enterprise case study on cloud-centric IoT transformations
\end{itemize}
}

% ================ PROFESSIONAL EXPERIENCE ================
\section*{PROFESSIONAL EXPERIENCE}

\entry{\textbf{Jan -- Jul 2025}}{%
\textbf{Software Engineer}, i-Vantage Technology, Lagos, Nigeria.
\begin{itemize}[leftmargin=*, nosep, itemsep=1pt]
    \item Automated secure software deployment using CI/CD pipelines with vulnerability scanning
    \item Hardened AWS cloud infrastructure (99.9\% uptime, zero unauthorized access incidents)
\end{itemize}
}

\entry{\textbf{Jun -- Aug 2024}}{%
\textbf{Cybersecurity Intern}, Hacktify.
\begin{itemize}[leftmargin=*, nosep, itemsep=1pt]
    \item Executed black-box and gray-box vulnerability assessments on enterprise web applications
    \item Identified critical security flaws (SQL Injection, XSS, SSRF) with remediation strategies
\end{itemize}
}

% ================ TEACHING EXPERIENCE ================
\section*{TEACHING EXPERIENCE}

\entry{\textbf{Mar 2021 -- Jul 2023}}{%
\textbf{Volunteer Tutor \& Academic Team Lead}, Nigerian Association of Computing Students, JABU.
\begin{itemize}[leftmargin=*, nosep, itemsep=1pt]
    \item Facilitated tutorials on Security Engineering and Communication Networks
    \item Courses: \textit{CS 314 (Security Engineering), CS 220 (Communication Networks)}
\end{itemize}
}

\entry{\textbf{Jul -- Nov 2022}}{%
\textbf{Technical Instructor}, JIT Solutions Technology.
\begin{itemize}[leftmargin=*, nosep, itemsep=1pt]
    \item Instructed 50 students in Web Technologies (JavaScript, TypeScript)
    \item Integrated security fundamentals (input validation, XSS prevention, secure authentication)
\end{itemize}
}

% ================ PUBLICATIONS ================
\section*{PUBLICATIONS}

\entry{2024}{%
Olutayo, V.A., \& \textbf{Ogunmola, M.A.} ``An Enhanced Courseware Accessibility Mobile-Based Learning System Model.'' \textit{African Journal of Information Systems}. (Manuscript).
}

\entry{2024}{%
Adeniran, A.O., Onuajah, S.I., Adeniran, A.A., \& \textbf{Ogunmola, M.A.} ``Implementing Cloud-Centric IoT Transformations: Merits and Demerits.'' \textit{Systemic Analytics}, 2(2), 174--187.
}

% ================ CONFERENCES AND SEMINARS ================
\section*{CONFERENCES AND SEMINARS}

\entry{Nov 2024}{%
Attendee, 6th International Conference on Cybersecurity and Cloud, Comercio.
}

\entry{Jul 2024}{%
Attendee, IoT West Africa Conference \& Exhibition, Lagos, Nigeria.
}

\entry{Jun 2023}{%
Presenter, Seminar, Joseph Ayo Babalola University — ``Improving the Accessibility of Academic Resources in Education Institutions.''
}

% ================ HONORS AND AWARDS ================
\section*{HONORS AND AWARDS}

\entry{2025}{%
University of Utah Graduate Fellowship.
}

\entry{2024}{%
EducationUSA Opportunity Funds Award.
}

\entry{2023}{%
\textbf{Overall Best Graduating Student (Valedictorian)}, Joseph Ayo Babalola University; Dean's Prize; University Scholar; Pro Chancellor's Prize; Parent Forum's Prize; Most Outstanding Student (Nigerian Association of Computing Students).
}

% ================ LEADERSHIP AND SERVICE ================
\section*{LEADERSHIP AND SERVICE}

\entry{\textbf{2025 -- Present}}{%
\textbf{Secretary}, Graduate Student Advisory Council (GradSAC), University of Utah.
}

\entry{\textbf{2024}}{%
\textbf{Community Organizer}, AWS Nigeria User Group.
}

\entry{\textbf{2024}}{%
\textbf{Member}, NYSC Medical Community Development Service Group.
}

\entry{\textbf{2022 -- 2023}}{%
\textbf{Team Leader}, NACOS JABU Academic Committee.
}

% ================ SKILLS ================
\section*{SKILLS}

\entry{\textbf{Security \& Privacy:}}{%
Confidential Computing (Intel SGX, Intel TDX, Gramine); Threat modeling; SIEM (Splunk, ELK); Penetration testing (Burp Suite, Nmap).
}

\entry{\textbf{Networking:}}{%
5G Core Networks; Open5GS; Wireshark; tcpdump.
}

\entry{\textbf{Cloud \& Distributed Systems:}}{%
Kubernetes; Docker; AWS; GCP; Azure; Terraform; CI/CD (Jenkins).
}

\entry{\textbf{Programming:}}{%
C; Python (Scikit-learn); JavaScript; TypeScript; React; React Native; ExpressJS; SQL; Java; Linux.
}

% ================ PROFESSIONAL AFFILIATIONS ================
\section*{PROFESSIONAL AFFILIATIONS}

\entry{}{%
Association for Computing Machinery. \\
IEEE Computer Society \\
National Society of Black Engineers \\
Society of Women Engineers
}

\end{document}
